### 2018-08-08 article.tex
typo and remarks
better example
homomorphism examples

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
  Given a free PROP of quantum circuits, we can extend it to a 2-PROP
    $\mathcal{P}$ where
  \begin{itemize}
    \item gates form the set of \emph{1-cells} 
    \item the \emph{2-cells} are generated by a finite set of \emph{rewriting}
      rules such that
    \begin{itemize}
      \item 2 rewriting rules with the same types must be equal
      \item each rewriting rule must be invertible, that is $\mathcal{C}(A, B)$
        is a \emph{groupoid} for all \emph{0-cells} $A, B$
    \end{itemize}
  \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM EXAMPLE        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{example}
  Let's take the previous quantum circuit example \ref{ex:quantum-circs} and add
    some \emph{noisy gates}, that is, gates which can failed with an $\epsilon$
    probability.
  \[
    \begin{array}{cccccccccc}
      \circZ{{\epsilon}} & \qquad  & \circX{{\epsilon}} & \qquad &
        \circbox{H_\epsilon} \\ 
      \vstrut{1.2em}
      Z_\epsilon : 1 \to 1 && X_\epsilon : 1 \to 1 && H_\epsilon : 1 \to 1
    \end{array}
  \]
  We form a 2-PROP by adding some rewriting rules (we omit the identies)
  \[
    \begin{array}{cccccccc}
      \circZ{{\epsilon}} & \Rightarrow & \circZ{{}} & \alpha : Z_\epsilon \to Z \\
      \vstrut{1.2em} \\
      \circX{{\epsilon}} & \Rightarrow & \circX{{}} & \beta : X_\epsilon \to X \\
      \vstrut{1.2em} \\
      \circbox{H_\epsilon} & \Rightarrow & \circH & \gamma : H_\epsilon \to H
    \end{array}
  \]
  Then, on the circuit
  \[
    \begin{array}{cccccccccc}
      \circbox{H_\epsilon} \\ 
      \vstrut{1.2em} \\
      \circZ{{\epsilon}}
    \end{array}
  \]
  a rewriting sequence can be $(id_{H_\epsilon} \otimes \alpha) \bullet (\beta
    \otimes id_Z)$
  \[
    \begin{array}{cccccccccc}
      \circbox{H_\epsilon} & \overset{id_{H_\epsilon}}{\Rightarrow} &
        \circbox{H_\epsilon} & \overset{\beta}{\Rightarrow} & \circH \\ 
      \vstrut{1.2em} \\
      \circZ{{\epsilon}} & \overset{\alpha}{\Rightarrow} & \circZ{{}} &
        \overset{id_Z}{\Rightarrow} & \circZ{{}} \\ 
    \end{array}
  \]
  Moreover this sequence is atomic.
\end{example}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
  For all $(A, B) \in \mathcal{P}$ we define a homomorphism $V:
    \mathcal{C}(A, B) \to \mathbb{Q}$, such that for all gates $f$
  \[
    V(f) \in \mathbb{Q}
  \]
  For all rewriting rules $\alpha: f \Rightarrow g$
  \[
    V(\alpha) = V(f) \oplus V(g)^{-1}
  \]

@@

  On rewriting sequences
  \begin{align}
    V(\alpha \circ \beta) &= V(\alpha) \oplus V(\beta) \\
    V(\alpha \otimes \beta) &= V(\alpha) \oplus V(\beta) \\
    V(\alpha \bullet \beta) &= V(\alpha) \oplus V(\beta)
  \end{align}
\end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 1 COROLLARY        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
  For all rewriting sequences $\alpha: f \Rightarrow g$, then $V(\alpha) = V(f)
    \oplus V(g)^{-1}$.
  Note that the definition of $V$ gives that only for rewriting rules.
\end{corollary}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
  Given a free PROP of quantum circuits, we can extend it to a 2-PROP
    $\mathcal{P}$ where
  \begin{itemize}
    \item gates form the set of \emph{1-cells} 
    \item the \emph{2-cells} are generated by a finite set of \emph{rewriting}
      rules such that
    \begin{itemize}
      \item 2 rewriting rules with the same types must be equal
      \item each rewriting rule must be invertible, that is $\mathcal{P}(A, B)$
        is a \emph{groupoid} for all \emph{0-cells} $A, B$
    \end{itemize}
  \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM EXAMPLE        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\circuitExample}[3]{\inline{%
\begin{tikzpicture}[circuit]
 \node (0) at (0, 0.5) {};
 \node [box] (2) at (1, 0.5) {#1};
 \node (4) at (3, 0.5) {};
 \draw (0) to (2);
 \draw (2) to (4);

 \node (1) at (0, -0.5) {};
 \node [box] (3) at (1, -0.5) {#2};
 \node [box] (5) at (2, -0.5) {#3};
 \node (6) at (3, -0.5) {};
 \draw (1) to (3);
 \draw (3) to (5);
 \draw (5) to (6);
\end{tikzpicture}
}}
\begin{example}
  Let's take the previous quantum circuit example \ref{ex:quantum-circs} and add
    some \emph{noisy gates}, that is, gates which can failed with an $\epsilon$
    probability.
  \[
    \begin{array}{cccccccccc}
      \circZ{{\epsilon}} & \qquad  & \circX{{\epsilon}} & \qquad &
        \circbox{H_\epsilon} \\ 
      \vstrut{1.2em}
      Z_\epsilon : 1 \to 1 && X_\epsilon : 1 \to 1 && H_\epsilon : 1 \to 1
    \end{array}
  \]
  We form a 2-PROP by adding some rewriting rules (we omit the identies)
  \[
    \begin{array}{cccccccc}
      \circZ{{\epsilon}} & \Rightarrow & \circZ{{}} & \alpha : Z_\epsilon
        \Rightarrow Z \\
      \vstrut{1.2em} \\
      \circX{{\epsilon}} & \Rightarrow & \circX{{}} & \beta : X_\epsilon
        \Rightarrow X \\
      \vstrut{1.2em} \\
      \circbox{H_\epsilon} & \Rightarrow & \circH & \gamma : H_\epsilon
        \Rightarrow H
    \end{array}
  \]
  Then, on the circuit
  \[
    \circuitExample{$H_\epsilon$}{$Z_\epsilon$}{$X$}
  \]
  a rewriting sequence can be $(id_{H_\epsilon} \otimes \alpha) \bullet (\beta
    \otimes id_Z) \circ (id \otimes id_X)$ \REM{I'm not sure of the sequence}
  \[
    \circuitExample{$H_\epsilon$}{$Z_\epsilon$}{$X$}
    \xRightarrow{id_{H_\epsilon} \otimes \alpha}
    \circuitExample{$H$}{$Z_\epsilon$}{$X$}
    \xRightarrow{\beta \otimes id_Z}
    \circuitExample{$H$}{$Z$}{$X$}
  \]
  Moreover this sequence is atomic.
\end{example}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
  For all $(A, B) \in \mathcal{P}$ we define a homomorphism $V:
    \mathcal{P}(A, B) \to \mathbb{Q}$, such that for all gates $f$
  \[
    V(f) \in \mathbb{Q}
  \]

@@

  On rewriting sequences
  \begin{align}
    V(\alpha \circ \beta) &= V(\alpha) \oplus V(\beta) \\
    V(\alpha \otimes \beta) &= V(\alpha) \oplus V(\beta) \\
    V(\alpha \bullet \beta) &= V(\alpha) \oplus V(\beta)
  \end{align}

  We all required that for all rewriting rules $\alpha: f \Rightarrow g$
  \[
    V(\alpha) = V(f) \oplus V(g)^{-1}
  \]

\end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 1 COROLLARY        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
  For all rewriting sequences $\alpha: f \Rightarrow g$, then $V(\alpha) = V(f)
    \oplus V(g)^{-1}$.
  Note that the homomorphism $V$ is now well defined
\end{corollary}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM EXAMPLES        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{example}[Gates counter]
  Let's start with a simple example, a gates counter homomorphism $N$ over the
    quantale the additive group of natural numbers.
  \begin{align*}
    N(f) & = 1 \\
    N(f \circ g) &= N(f) + N(g) \\
    N(f \otimes g) &= N(f) + N(g)
  \end{align*}
  On rewriting sequences we have
  \[
    N(f \Rightarrow g) = N(f) - N(g)
  \]
  Then the induced $\mathbb{Q}$-enriched category become a tool which give us
    the number of gates added or removed given a rewriting sequence.
\end{example}

\begin{example}[Depth \& time counters]
  Two similar counters can be made using the depth and the time of a circuit
  \begin{align*}
    D(f) &= 1 \\
    D(f \circ g) &= D(f) + D(g) \\
    D(f \otimes g) &= \max(D(f), D(g))
  \end{align*}
  and
  \begin{align*}
    T(f) &= t_f \\
    T(f \circ g) &= T(f) + T(g) \\
    T(f \otimes g) &= \max(T(f), T(g))
  \end{align*}
  With $t_f$ defined for the generators of the PROP.
  It is easily to check that
  \begin{align*}
    \max(D(f), D(g)) \preceq D(f) + D(g)
    \max(T(f), T(g)) \preceq T(f) + T(g)
  \end{align*}
  as required by the homomorphism.
\end{example}
